Influences of GDP in the U.S

### 2022-11-12 Manuscript/manuscript.tex
commit

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{multirow}

\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

% made centered
$C + I + G + NX = GDP$

@@

@@

>>>>

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{multirow}
\usepackage{setspace}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

\doublespacing

@@

\begin{equation}
C + I + G + NX = GDP
\end{equation}

@@

To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
Multiple linear regrssion is a continuation of simple linear regression. 
For this model, there must be two or more independent predictors that are used to predict one dependent variable. 
The general form of the multiple linear regression model is as follows:

\begin{equation}
  Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + ... + \beta_n X_n + \epsilon
\end{equation}

In this equation, Y is an outcomes that is a continuous measurement. $\beta_0$ is the intercept, $\beta_1 X_1$ is the regression coefficent of the first independent variable. 
$\beta_n X_n$ is the last regression coefficent for the final variable in the model.
$\epsilon$ represents how much variation there is in our estimate for the dependent variable, or otherwise known as model error.

@@

When applying multiple linear regression to the data set, all independent variables were included in the intital model.
The model was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the traing dataset.

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{AVP1}
\end{figure}
